---
#title: "Peer Assesment 1"
##author: "Santiago Armida"
##date: "12 de junio de 2015"
###output: html_document
---

The variables included in this dataset are:
  steps: Number of steps taking in a 5-minute interval (missing values are coded as NA)
  date: The date on which the measurement was taken in YYYY-MM-DD format
  interval: Identifier for the 5-minute interval in which measurement was taken
The dataset is stored in a comma-separated-value (CSV) file and there are a total of 17,568 observations in this dataset.

For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

#  Reproductible Research
# by Santiago Armida: June 14, 2015
## read data and setup envirnment
# setwd("~/Documents/Data Science 5") it will read the data in current directory

```{r}
#Install and load libraries
    library(plyr)
#Install can be comented (#) if the package is already down
# packages to solve question via SQL
    install.packages("sqldf")
    library(sqldf)
## read data
    setwd("~/Documents/Data Science 5")
    acts <- read.csv("activity.csv")
```
Calculate the mean and total steps per day
```{r, echo=FALSE}
stepdata <- sqldf("select date, avg(steps) as avgstep, sum(steps) as sumsteps from acts where steps <> 'NA' group by date")
# nrow(NEIYEAR)
```
You can also embed plots, for example:

```{r, echo=FALSE}
hist(stepdata$sumsteps)
```

Another chunk, not displayed
```{r simultation, echo=FALSE}
set.seed(1)
x <- rnorm(100)
mean(x)
````
Randoms
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
